---
title: "data-enginering"
author: "Jan Besler"
date: "`r Sys.Date()`"
output: html_document
---

# libraries

```{r setup, echo=FALSE}
# load libraries
library(knitr)      # use .Rmd files

  # reading data
library(readr)      # reading csv
library(data.table) # fast data manipulation
library(readxl)

  # manipulate data
library(tidyr)      # manipulating data
library(dplyr)      # manipulating data
library(rlist)      # working with lists
library(stringr)    # work with strings
library(tibble)     # create data frames
library(stringi)    # process charactar strings
library(lubridate)  # transform character into dates
library(epitools)   # time manipulation
library(lubridate)  # time manipulation (quarters)
library(diffdf)     # compare df
library(useful)     # shift columns
library(anytime)    # convert to time easily

  # statistics
library(Matrix)     # required for lme4

  # visuals
library(ggplot2)    # make graphs
library(ggExtra)    # additional functionality for ggplot2
library(ggpubr)     # combine multiple graphs into one
library(gridExtra)  # table management
```

# load raw data

explanations for the acronyms & adress

  - HuN = Haid-und-Neu-Straße
  - HuN 32 = Mehrgenerationen Haus
  - HuN 18 = Hoepfner Areal
  - HuN 5a = FZI
  - HuN 14 = FZI
  - HuN 7  = TechnologieFarbik
  
  

>**UTC time and german time have not always a lag of 1 hour.** This comes down to the use of summer and winter time. Both time stamps are carried through to look for differences later in the graphs.

### MGH

The MGH data has to be shifted by 15 minutes, because the measured points occur at the end of the 15 minute mark. 

```{r data MGH}
# define col names to avoid UTF-8 errors
col_names <- c("Tag_deutsch",
             "Tag_UTC",
             "Bezug_kumuliert_Wh",
             "Einspeisung_kumuliert_Wh",
             "Bezug_W",
             "Einspeisung_W")

# load data for MGH
  # december 2019
raw_MGH_19 <- fread(
  "./data/Lastgaenge/Rohdaten/HuN 32 - 08135284 - Ъbergabe - ZДhler 2019_Dez.csv",
  col.names = col_names
)
  
raw_MGH_20 <- fread(
  "./data/Lastgaenge/Rohdaten/HuN 32 - 08135284 - Ъbergabe - ZДhler 2020.csv"
)
head(raw_MGH_20, n = 1)[[1]]
tail(raw_MGH_20, n = 1)[[1]]

  # whole 2021 data
raw_MGH_21 <- fread(
  "./data/Lastgaenge/Rohdaten/HuN 32 - 08135284 - Ъbergabe - ZДhler 2021.csv",
  col.names = col_names
)
head(raw_MGH_21, n = 1)[[1]]
tail(raw_MGH_21, n = 1)[[1]]

  # january - march 21st data 2021
raw_MGH_22 <- fread(
  "./data/Lastgaenge/Rohdaten/HuN 32 - 08135284 - Ъbergabe - ZДhler 2022_Jan-Mrz.csv",
  col.names = col_names
)
head(raw_MGH_22, n = 1)[[1]]
tail(raw_MGH_22, n = 1)[[1]]

  # add UTC time
    # first change last measures from prvious year
Tag_2020 <- str_replace_all(raw_MGH_21$Tag_UTC, "2020", "2019")
    # then change all the rest of the data
Tag_2020 <- str_replace_all(Tag_2020, "2021", "2020")
    # get 29th february
feb_29th <- raw_MGH_20[grep("29.02.", raw_MGH_20$Zeit)]$Zeit

    # insert 29th into vector
Tag_2020 <- append(
  Tag_2020,
  feb_29th,
  after = which(Tag_2020 == '28.02.2020 23:45'))

    # delete 31st december to cut to length of 35040
Tag_2020 <- Tag_2020[1:35040]
    # add to data frame
raw_MGH_20$Tag_UTC <- Tag_2020
  # change col order and colnames
raw_MGH_20 <- raw_MGH_20 %>% relocate(
  Tag_UTC, .after = Zeit)
  colnames(raw_MGH_20) <- col_names

# merge data - since the data connects perfectly, they only have to be appended
raw_clean_MGH <- rbindlist(list(raw_MGH_19, raw_MGH_20, raw_MGH_21, raw_MGH_22),
                           use.names = TRUE  # bind by colnames
                           )
```

Since the base data is merged now, the manipulation process is started.

```{r MGH_manipulation}
# move time 15 one lag to start on 13:45
  # german time
raw_clean_MGH$Tag_deutsch[2:nrow(raw_clean_MGH)] <- raw_clean_MGH$Tag_deutsch[1:(nrow(raw_clean_MGH) - 1)]
  # UTC time
raw_clean_MGH$Tag_UTC[2:nrow(raw_clean_MGH)] <- raw_clean_MGH$Tag_UTC[1:(nrow(raw_clean_MGH) - 1)]
  # change first values
raw_clean_MGH[1,1:2] <- list("02.12.2019 14:45", "02.12.2019 13:45")

# counting unique values in table
aggregate(data.frame(count = raw_clean_MGH$Einspeisung_W),
          list(value = raw_clean_MGH$Einspeisung_W),
          length)
  # here it can be seen that most of the values are 0, but ~ 8000 values > 0.

# change column types from character to date
  # change to date
raw_clean_MGH$Tag_deutsch <- dmy_hm(raw_clean_MGH$Tag_deutsch, tz = grep("Berlin", OlsonNames(), value = TRUE))
raw_clean_MGH$Tag_UTC <- dmy_hm(raw_clean_MGH$Tag_UTC, tz = "UTC")

# write csv file
write_csv(
  x = raw_clean_MGH,
  file = "./data/MGH_raw.csv",
  append = FALSE,
  col_names = TRUE
  )

# check for differences between Johannes and this file.
  # load the data
predone_data <- fread(
  "./data/Lastgaenge/Lastgang MGH 2019-2022 UTC Broken.csv",
  col.names = c("Tag_UTC", "Bezug_W")
)
  # subset data to compare
raw_compare <- raw_clean_MGH[, c("Tag_UTC", "Bezug_W")]
  # check for differences and similarities
diffdf(raw_compare, predone_data, suppress_warnings = TRUE)

# 31st december 2020, missing in data

# collect garbage
rm(
  predone_data,
  raw_compare
  )
gc()
```

### Hoepfner

For the Hoepfner data the 29th february 2020 is included, though the 31st december 2020 is missing here too.

Data again lists the values for the end of the 15-minutes time frame.

```{r data Hoepfner}
# load data for Hoepfner - seperated into 2 locations & files

  # whole 2020 data
raw_Hoepfner_20 <- fread(
  "./data/Lastgaenge/Rohdaten/BES - HuN Str. 18 - 08579175 - ZДhler 08579175_2020.csv",
  col.names = col_names
)
head(raw_Hoepfner_20, n = 1)[[1]]
tail(raw_Hoepfner_20, n = 1)[[1]]

  # whole 2021 data
raw_Hoepfner_21 <- fread(
  "./data/Lastgaenge/Rohdaten/BES - HuN Str. 18 - 08579175 - ZДhler 08579175_2021.csv",
  skip = 2,  # comment in first line
  col.names = col_names
)
head(raw_Hoepfner_21, n = 1)[[1]]
tail(raw_Hoepfner_21, n = 1)[[1]]

  # whole 2022 data
raw_Hoepfner_22 <- fread(
  "./data/Lastgaenge/Rohdaten/BES - HuN Str. 18 - 08579175 - ZДhler 08579175_2022.csv",
  col.names = col_names
)
head(raw_Hoepfner_22, n = 1)[[1]]
tail(raw_Hoepfner_22, n = 1)[[1]]

# analyse data
  # difference in two data sets
nrow(raw_Hoepfner_20) - nrow(raw_Hoepfner_21)
  # one day is missing!
# find missing day
days_2020 <- substr(raw_Hoepfner_20$Tag_UTC, start = 1, stop = 6)
days_2021 <- substr(raw_Hoepfner_21$Tag_UTC, start = 1, stop = 6)
setdiff(days_2020, days_2021)

# only difference is 29th February, hence 31st December is also missing again

# merge data
raw_clean_Hoepfner <- rbindlist(list(
  raw_Hoepfner_20,
  raw_Hoepfner_21,
  raw_Hoepfner_22),
  use.names = TRUE)

# move time 15 one lag to start on 13:45
# german time
raw_clean_Hoepfner$Tag_deutsch[2:nrow(raw_clean_Hoepfner)] <-
  raw_clean_Hoepfner$Tag_deutsch[1:(nrow(raw_clean_Hoepfner) - 1)]
# UTC time
raw_clean_Hoepfner$Tag_UTC[2:nrow(raw_clean_Hoepfner)] <-
  raw_clean_Hoepfner$Tag_UTC[1:(nrow(raw_clean_Hoepfner) - 1)]
# change first values
raw_clean_Hoepfner[1, 1:2] <-
  list("01.01.2020 00:00", "31.12.2019 23:00")

# change column types from character to date
  # change to date
raw_clean_Hoepfner$Tag_deutsch <- dmy_hm(raw_clean_Hoepfner$Tag_deutsch, tz = grep("Berlin", OlsonNames(), value = TRUE))
raw_clean_Hoepfner$Tag_UTC <- dmy_hm(raw_clean_Hoepfner$Tag_UTC, tz = "UTC")

# set impossible data to NaN
raw_clean_Hoepfner[raw_clean_Hoepfner$Bezug_W == 0,]
count(raw_clean_Hoepfner[raw_clean_Hoepfner$Bezug_W == 0,])


# write csv file
write_csv(
  x = raw_clean_Hoepfner,
  file = "./data/Hoepfner_raw.csv",
  append = FALSE,
  col_names = TRUE
  )


# # compare with Johannes solution
# predone_data <- rbindlist(list(
#   fread("./data/Lastgaenge/Lastgang Hoepfner 2020 UTC Broken.csv",
#   col.names = c("Tag_UTC", "Bezug_W")),
#   fread("./data/Lastgaenge/Lastgang Hoepfner 2021 UTC Full.csv",
#   col.names = c("Tag_UTC", "Bezug_W")),
#   fread("./data/Lastgaenge/Lastgang Hoepfner 2022 UTC Broken.csv",
#   col.names = c("Tag_UTC", "Bezug_W"))
# ))
# missing_Hoepfner <- setdiff(
#   substr(predone_data$Tag_UTC, start = 1, stop = 10),
#   substr(raw_clean_Hoepfner$Tag_UTC, start = 1, stop = 10)
# )
# length(missing_Hoepfner)
# missing_Hoepfner

# collect garbage
rm(
  missing_Hoepfner,
  predone_data,
  days_2020,
  days_2021
)
```
All of 31st Decembers is missing in pre-processed data. Plus 69 data points from 13.07.2020 show no energy usage.

### FZI

##### HuN 5a

```{r data FZI}
# load data for FZI - seperated into 2 locations & files

# first part for HuN 5a
  # whole 2019 data
raw_FZI_19_1 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2019_Lastgang_FZI_Anlage 1712_Marktlokation 50784599465_Haid-und_Neu-Str. 5a.xlsx",
  skip = 1
)
raw_FZI_19_1$...4 = NULL  # deletes comments in fourth column
head(raw_FZI_19_1, n = 1)[[1]]
tail(raw_FZI_19_1, n = 1)[[1]]

  # whole 2020 data
raw_FZI_20_1 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2020_Lastgang_FZI_Anlage 1712_Marktlokation 50784599465_Haid-und_neu-Str. 5a.xlsx",
  skip = 1
)
head(raw_FZI_20_1, n = 1)[[1]]
tail(raw_FZI_20_1, n = 1)[[1]]

  # whole 2021 data
raw_FZI_21_1 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2021_Lastgang_FZI_Anlage 1712_Marktlokation 50784599465_Haid-und_neu-Str. 5a.xlsx",
  skip = 1
)
head(raw_FZI_21_1, n = 1)[[1]]
tail(raw_FZI_21_1, n = 1)[[1]]

# merge files
raw_FZI_1 <- rbindlist(list(
   raw_FZI_19_1,
   raw_FZI_20_1,
   raw_FZI_21_1),
   use.names = TRUE)
setnames(raw_FZI_1, c('Ab-Datum', 'Ab-Zeit', 'Profilwert kW'), c('Datum', 'Zeit', 'Bezug_W'))

# change column from kW to W
raw_FZI_1$Bezug_W <- raw_FZI_1$Bezug_W * 1000

# change time format
raw_FZI_1$Zeit <- substr(raw_FZI_1$Zeit, start = 12, stop = 16)
raw_FZI_1$Datum <- strftime(raw_FZI_1$Datum, format = "%d.%m.%Y")
raw_FZI_1$Zeit_deutsch <- paste(raw_FZI_1$Datum, raw_FZI_1$Zeit, sep = " ")
```

##### HuN 14

repeat for 2nd half of data

not included anymore since there is no legal ground to use this data!

```{r FZI_2, eval=FALSE}
# second part HuN 14
  # 2019 data
raw_FZI_19_2 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2019_Lastgang_FZI_Anlage 1719_Marktlokation 50782704165_Haid-und_neu-Str. 14.xlsx",
  skip = 1
)
head(raw_FZI_19_2, n = 1)[[1]]
tail(raw_FZI_19_2, n = 1)[[1]]

  # 2020 data
raw_FZI_20_2 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2020_Lastgang_FZI_Anlage 1719_Marktlokation 50782704165_Haid-und_neu-Str. 14.xlsx",
  skip = 1
)
head(raw_FZI_20_2, n = 1)[[1]]
tail(raw_FZI_20_2, n = 1)[[1]]

  # 2021 data
raw_FZI_21_2 <- read_excel(
  "./data/Lastgaenge/Rohdaten/2020_Lastgang_FZI_Anlage 1719_Marktlokation 50782704165_Haid-und_neu-Str. 14.xlsx",
  skip = 1
)
head(raw_FZI_21_2, n = 1)[[1]]
tail(raw_FZI_21_2, n = 1)[[1]]

# merge files
raw_FZI_2 <- rbindlist(list(
   raw_FZI_19_2,
   raw_FZI_20_2,
   raw_FZI_21_2),
   use.names = TRUE)
setnames(raw_FZI_2, c('Ab-Datum', 'Ab-Zeit', 'Profilwert kW'), c('Datum', 'Zeit', 'Bezug_kW'))

# change time format
raw_FZI_2$Zeit <- substr(raw_FZI_2$Zeit, start = 12, stop = 16)
raw_FZI_2$Datum <- strftime(raw_FZI_2$Datum, format = "%d.%m.%Y")
raw_FZI_2$Zeit_deutsch <- paste(raw_FZI_2$Datum, raw_FZI_2$Zeit, sep = " ")
```

##### merge & manipulation

now combine both files and start manipulating the data.

```{r FZI combined, eval=FALSE}
# analyse differences
missing_FZI <- setdiff(
  raw_FZI_2$Datum,
  raw_FZI_1$Datum
)
length(missing_FZI)
missing_FZI

# first three months of 2019 are missing for first part

# merge two data sets
raw_clean_FZI <- full_join(
  raw_FZI_1,
  raw_FZI_2,
  by = c("Datum", "Zeit", "Zeit_deutsch")
)
setnames(raw_clean_FZI, c('Bezug_kW.x', 'Bezug_kW.y'), c('HuN_5a', 'HuN_14'))

# relocate german time column
raw_clean_FZI <- raw_clean_FZI %>% relocate(
  Zeit_deutsch, .after = Zeit)

# move time 15 one lag to start on 13:45
# german time
raw_clean_Hoepfner$Tag_deutsch[2:nrow(raw_clean_Hoepfner)] <-
  raw_clean_Hoepfner$Tag_deutsch[1:(nrow(raw_clean_Hoepfner) - 1)]
# UTC time
raw_clean_Hoepfner$Tag_UTC[2:nrow(raw_clean_Hoepfner)] <-
  raw_clean_Hoepfner$Tag_UTC[1:(nrow(raw_clean_Hoepfner) - 1)]
# change first values
raw_clean_Hoepfner[1, 1:2] <-
  list("01.01.2020 00:00", "31.12.2019 23:00")

# missing values in columns
sum(is.na(raw_clean_FZI$HuN_5a))
sum(is.na(raw_clean_FZI$HuN_14))
  # print row of single missing value
raw_clean_FZI[(which(is.na(raw_clean_FZI$HuN_14))-2):(which(is.na(raw_clean_FZI$HuN_14))+2),]

# output shows shift in profiling of 15 minutes
  # normalising on second row and startign values of 15 minutes
raw_clean_FZI <- raw_clean_FZI %>% mutate_at(c("HuN_5a"),
                         lead,
                         n = 1)

# drop row with missing value
raw_clean_FZI <- drop_na(raw_clean_FZI,HuN_14)

# build sum where both data sets are complete
raw_clean_FZI$Summe_Verbrauch <- rowSums(
  raw_clean_FZI[, 4:5],  # add 3rd & 4th column
  na.rm = FALSE
)

# subset data with both entries
raw_clean_FZI_small <- subset(raw_clean_FZI, !is.na(raw_clean_FZI$Summe_Verbrauch))
  # delete dulicated entries
raw_clean_FZI_small <- raw_clean_FZI_small[!duplicated(raw_clean_FZI_small),]


# change column types from character to date
  # change to date
raw_clean_FZI_small$Zeit_deutsch <- dmy_hm(raw_clean_FZI_small$Zeit_deutsch, tz = grep("Berlin", OlsonNames(), value = TRUE))

# write csv file
write_csv(
  x = raw_clean_FZI_small,
  file = "./data/FZI_raw.csv",
  append = FALSE,
  col_names = TRUE
  )

# collect garbage
rm(
  raw_FZI_1,
  raw_FZI_2,
  missing_FZI
)
gc()
```

only continue working with FZI_1 data!

```{r FZI_manipulation}
# move time 15 one lag to start on 13:45
# german time
raw_FZI_1$Zeit_deutsch[2:nrow(raw_FZI_1)] <-
  raw_FZI_1$Zeit_deutsch[1:(nrow(raw_FZI_1) - 1)]
# change first values
raw_FZI_1$Zeit_deutsch[[1]] <-
  "01.04.2019 00:00"

# missing values in columns
sum(is.na(raw_FZI_1$Bezug_kW))

# change column types from character to date
  # change to date
raw_FZI_1$Zeit_deutsch <- dmy_hm(raw_FZI_1$Zeit_deutsch, tz = grep("Berlin", OlsonNames(), value = TRUE))

# write csv file
write_csv(
  x = raw_FZI_1,
  file = "./data/FZI_raw.csv",
  append = FALSE,
  col_names = TRUE
  )

# collect garbage
# rm(
#   raw_FZI_19_1,
#   raw_FZI_20_1,
#   raw_FZI_21_1
# )
# gc()
```


### TeFak

```{r TeFak}
# monthly based reading
TeFak_cols = c("Datum", "von", "Leistung in kW")
TeFak_csv <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11")
raw_TeFak <- as.data.frame(matrix(data = NA,
                                  ncol = 2,
                                  nrow = 1))
colnames(raw_TeFak) <- c("Datum", "Leistung in W")
for(i in TeFak_csv) {
  raw <- fread(
      paste0("~/Uni/KIT - Advanced Topics/data/Lastgaenge/Rohdaten/Technologiefabrik/2020.", i, "_368510_Technologiefabrik Karlsruhe GmbH_1.csv"),
      skip = 9,
      select = TeFak_cols
    )
  raw$Datum <- paste(raw$Datum, raw$von, sep = " ")
  raw$`Leistung in W` <-
    as.numeric(str_sub(raw$`Leistung in kW`, 1, nchar(raw$`Leistung in kW`) - 4)) * 1000
  raw[, 2:3] <- NULL
  raw_TeFak <- rbind(raw_TeFak, raw)
}
raw_TeFak <- raw_TeFak[-1,]
raw_TeFak$Datum <- dmy_hm(raw_TeFak$Datum, tz = grep("Berlin", OlsonNames(), value = TRUE))
# load december
raw_TeFak_12 <- readxl::read_xlsx("~/Uni/KIT - Advanced Topics/data/Lastgaenge/Rohdaten/Technologiefabrik/Lastgang Dezember 2020 - VK 220001937.xlsx",
                                  skip = 2)
raw_TeFak_12$Datum <- paste(raw_TeFak_12$`Ab-Datum`,
                            str_sub(raw_TeFak_12$`Ab-Zeit`, -8, -1),
                            sep = " ")
raw_TeFak_12$`Leistung in W` <- raw_TeFak_12$kW * 1000
raw_TeFak_12[, 1:3] <- NULL

raw_TeFak <- rbind(raw_TeFak, raw_TeFak_12)

```


# combine to data

```{r data_export}
data <- full_join(
  full_join(
    full_join(
      select(raw_clean_Hoepfner, Tag_deutsch, Bezug_W)[2:nrow(raw_clean_Hoepfner), ],
      select(raw_clean_MGH, Tag_deutsch, Bezug_W),
      by = "Tag_deutsch"
    ),
    select(raw_FZI_1, Zeit_deutsch, Bezug_W),
    by = c("Tag_deutsch" = "Zeit_deutsch")
  ),
  raw_TeFak,
  by = c("Tag_deutsch" = "Datum")
)
class(data$Tag_deutsch)
# order by date
data <- arrange(data, Tag_deutsch)

# rename columns
colnames(data) <- c("Zeit_deutsch", "Hoepfner", "MGH", "FZI", "TeFak")

# save data frame
write_csv(
  data,
  file = "./data/data_clean.csv"
)
```

# Gantt Diagram

make a graph to show which time frame the single files cover.

```{r gantt, eval=FALSE}
# table for gantt chart
gantt_df <- data.frame(matrix(NA,
                               nrow = 13,  # as many rows as individual files
                               ncol = 3))  # 3 columns for building, start and end
gantt_df <- dplyr::rename(
    gantt_df,
    'data_input' = X1,
    'start' = X2,
    'end' = X3
  )
# name the tasks
raw_names_vec <- c(
  "raw_MGH_19",
  "raw_MGH_20",
  "raw_MGH_21",
  "raw_MGH_22",
  "raw_Hoepfner_20",
  "raw_Hoepfner_21",
  "raw_Hoepfner_22",
  "raw_FZI_19_1",
  "raw_FZI_20_1",
  "raw_FZI_21_1",
  "raw_FZI_19_2",
  "raw_FZI_20_2",
  "raw_FZI_21_2"
)
gantt_df[,1] <- raw_names_vec

raw_data_vec <- c(
  raw_MGH_19[,1],
  raw_MGH_20[,1],
  raw_MGH_21[,1],
  raw_MGH_22[,1],
  raw_Hoepfner_20[,1],
  raw_Hoepfner_21[,1],
  raw_Hoepfner_22[,1],
  raw_FZI_19_1[,1],
  raw_FZI_20_1[,1],
  raw_FZI_21_1[,1]
  # raw_FZI_19_2[,1],
  # raw_FZI_20_2[,1],
  # raw_FZI_21_2[,1]
)

for (j in 1:7) {
  gantt_df[j, 2] <-
    substr(raw_data_vec[[j]][1], start = 1, stop = 10)  # start
  gantt_df[j, 3] <-
    substr(raw_data_vec[[j]][lengths(raw_data_vec)[j]], start = 1, stop = 10)  # end
}
# for posixtc dates
gantt_df[8:length(raw_data_vec),2] <- c("01.04.2019", "01.01.2020", "01.01.2021", "01.01.2019", "01.01.2020", "01.01.2021")
gantt_df[8:length(raw_data_vec),3] <- c("01.01.2020", "01.01.2021", "01.01.2022", "01.01.2020", "01.01.2021", "01.01.2022")

# column class as Date
gantt_df$start <- anydate(gantt_df$start)
gantt_df$end <- anydate(gantt_df$end)
  # add missing values by hand
gantt_df$end[[2]] <- as.Date("2020-12-31")
gantt_df$end[[4]] <- as.Date("2022-03-21")
gantt_df$end[[5]] <- as.Date("2020-12-31")
gantt_df$end[[6]] <- as.Date("2021-12-31")

# add column for grouping
gantt_df$building <- c(rep("MGH",4), rep("Hoepfner",3), rep("FZI", 6))

# Gantt chart
ggplot(gantt_df,
       aes(
         x = start,
         xend = end,
         y = data_input,
         yend = data_input,
         color = building
       )) +
  theme_bw() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_blank(),
        axis.title.y = element_blank()) +
  geom_segment(size = 10) +
  labs(title = "Rohdaten nach Gebäuden",
       x = "Jahr",
       y = "none")

ggsave(filename = "Rohdatenverfügbarkeit.png",
       device = "png",
       path = "./graphs/",
       dpi = 320,
       width = 12,
       height = 6
)


```

# test field

```{r test}
rbind(raw_TeFak_1)

str_sub(raw_TeFak_12$`Ab-Zeit`, -8, -1)
```
