---
title: "basic analysis"
author: "Jan Besler"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

```{r setup, echo=FALSE}
# load libraries
library(knitr)      # use .Rmd files

  # reading data
library(readr)      # reading csv
library(data.table) # fast data manipulation
library(readxl)     # read in excel sheets

  # manipulate data
library(tidyr)      # manipulating data
library(dplyr)      # manipulating data
library(rlist)      # working with lists
library(stringr)    # work with strings
library(tibble)     # create data frames
library(stringi)    # process charactar strings
library(lubridate)  # transform character into dates
library(epitools)   # time manipulation
library(lubridate)  # time manipulation (quarters)

  # statistics
library(Matrix)     # required for lme4
library(tseries)    # time series properties

  # visuals
library(ggplot2)    # make graphs
library(ggExtra)    # additional functionality for ggplot2
library(ggpubr)     # combine multiple graphs into one
library(gridExtra)  # table management
library(patchwork)  # align multiple graphs
```

# data import

reading in different sheets from the excel table according to our needs

```{r import}
# read in BDEW excel table
  # H0
BDEW_H0 <- read_xls("./data/Profile_BDEW/ReprДsentative Profile VDEW.xls",
                      sheet = "H0",
                      skip = 3,
                      n_max = 96,
                      col_names = c("Time",
                                    "WiSa", "WiSo", "WiMoFr",
                                    "SoSa", "SoSo", "SoMoFr",
                                    "UeberSa", "UeberSo", "UeberMoFr"))
  # add hour column
BDEW_H0$hour <- as.integer(substr(BDEW_H0$Time, 12,13))
  
  # G1 - commercial workdays 8-18 o'clock
BDEW_G1 <- read_xls("./data/Profile_BDEW/ReprДsentative Profile VDEW.xls",
                      sheet = "G1",
                      skip = 3,
                      n_max = 96,
                      col_names = c("Time",
                                    "WiSa", "WiSo", "WiMoFr",
                                    "SoSa", "SoSo", "SoMoFr",
                                    "UeberSa", "UeberSo", "UeberMoFr"))
  # add hour column
BDEW_G1$hour <- as.integer(substr(BDEW_G1$Time, 12,13))

  # G5 - bakery
BDEW_G5 <- read_xls("./data/Profile_BDEW/ReprДsentative Profile VDEW.xls",
                      sheet = "G5",
                      skip = 3,
                      n_max = 96,
                      col_names = c("Time",
                                    "WiSa", "WiSo", "WiMoFr",
                                    "SoSa", "SoSo", "SoMoFr",
                                    "UeberSa", "UeberSo", "UeberMoFr"))
  # add hour column
BDEW_G5$hour <- as.integer(substr(BDEW_G5$Time, 12,13))

# load data from previous files
data <- read_csv("./data/predoneData.csv")
data$BDEW_Season <- ifelse(data$month >= 12 | data$month <= 2, "Winter",
              ifelse(data$month >= 6 & data$month <= 9, "Summer", "Uebergang"))
data$BDEW_week <- ifelse(data$dayOfWeek == "Sun", 3,
                         ifelse(data$dayOfWeek == "Sat", 2, 1))
data$hour <- as.integer(data$hour)
```


# complete graphs

all values have to be scaled to be compared with different magnitudes of measurements.

### function

```{r scaling}
# index values
scaledSeason <- function(data) {
  result <-
    vector(mode = "numeric", length = nrow(data))
  for (j in 2:ncol(data)) {
    for (i in 1:nrow(data)) {
      result[i] <- (data[i, j] - mean(data[,j], na.rm = TRUE)) / sd(data[,j], na.rm = TRUE)
    }
    data <- cbind(data, result)
    colnames(data)[j + 12] <-
      paste0(names(data)[j], "_ind")
  }
  return(data)
}
```

### mean

```{r BDEW_data}
# create matrix
compare_df <- matrix(data = NA,
                     ncol = 14,
                     nrow = 3*24)
# fill matrix
colnames(compare_df) <- c("Time", "Season",
                          "MoFrKIT", "SaKIT", "SoKIT",
                          "MoFrH0", "SaH0", "SoH0",
                          "MoFrG1", "SaG1", "SoG1",
                          "MoFrG5", "SaG5", "SoG5")
compare_df[,1] <- rep(seq(0,23,1), 3)
compare_df[1:24,2] <- rep("Winter", 24)
compare_df[25:48,2] <- rep("Summer", 24)
compare_df[49:72,2] <- rep("Transition", 24)

# fill with KIT data
daytypes <- c("MoFr", "Sa", "So")
for(j in 1:max(data$BDEW_week)) {
  # winter
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Winter" & data$BDEW_week == j, "MGH"]
    compare_df[i + 1, paste0(daytypes[j], "KIT")] <-
      mean(result[["MGH"]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Summer" & data$BDEW_week == j, "MGH"]
    compare_df[i + 25, paste0(daytypes[j], "KIT")] <-
      mean(result[["MGH"]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Uebergang" & data$BDEW_week == j, "MGH"]
    compare_df[i + 49, paste0(daytypes[j], "KIT")] <-
      mean(result[["MGH"]], na.rm = TRUE)
  }
}

# fill with BDEW data
  # H0
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("Wi", daytypes[j])]
    compare_df[i + 1, paste0(daytypes[j], "H0")] <-
      mean(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("So", daytypes[j])]
    compare_df[i + 25, paste0(daytypes[j], "H0")] <-
      mean(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("Ueber", daytypes[j])]
    compare_df[i + 49, paste0(daytypes[j], "H0")] <-
      mean(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}
  # G1
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("Wi", daytypes[j])]
    compare_df[i + 1, paste0(daytypes[j], "G1")] <-
      mean(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("So", daytypes[j])]
    compare_df[i + 25, paste0(daytypes[j], "G1")] <-
      mean(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("Ueber", daytypes[j])]
    compare_df[i + 49, paste0(daytypes[j], "G1")] <-
      mean(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}
  # G5
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("Wi", daytypes[j])]
    compare_df[i + 1, paste0(daytypes[j], "G5")] <-
      mean(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("So", daytypes[j])]
    compare_df[i + 25, paste0(daytypes[j], "G5")] <-
      mean(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("Ueber", daytypes[j])]
    compare_df[i + 49, paste0(daytypes[j], "G5")] <-
      mean(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}

# turn into data frame to use in ggplot
compare_df <- as.data.frame(compare_df)
for (i in 1:ncol(compare_df)){
  # skip for season column
  if(i == 2)
    next
  else
    compare_df[,i] <- as.numeric(compare_df[,i])
}

# create sub data frames
compare_all <- rbind(
  scaledSeason(compare_df[compare_df$Season == "Winter",-2]),
  scaledSeason(compare_df[compare_df$Season == "Summer",-2]),
  scaledSeason(compare_df[compare_df$Season == "Transition",-2])
)
compare_all$season <- compare_df$Season

# test for differences
t.test(compare_all$MoFrKIT_ind, compare_all$MoFrH0_ind)
t.test(compare_all$MoFrKIT_ind, compare_all$MoFrG1_ind)
t.test(compare_all$MoFrKIT_ind, compare_all$MoFrG5_ind)
```

### visualization

```{r bdew_graphs}
# Werktags
werktagsGraph <- ggplot(
  data = compare_all,
  aes(x = Time)) +
  geom_line(aes(y = MoFrH0_ind, color = "H0"), alpha = 0.3) +
  geom_line(aes(y = MoFrG1_ind, color = "G1"), alpha = 0.3) +
  geom_line(aes(y = MoFrG5_ind, color = "G5"), alpha = 0.7) +
  geom_line(aes(y = MoFrKIT_ind, color = "district")) +
  ggtitle("Weekdays") +
  theme_bw() +
  theme(legend.position = "none",
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  labs(x = "Time of day") +
  facet_grid(as.factor(season) ~ .,
             switch = "y")

# Samstag
samstagGraph <- ggplot(
  data = compare_all,
  aes(x = Time)) +
  geom_line(aes(y = SaH0_ind, color = "H0"), alpha = 0.3) +
  geom_line(aes(y = SaG1_ind, color = "G1"), alpha = 0.6) +
  geom_line(aes(y = SaG5_ind, color = "G5"), alpha = 0.6) +
  geom_line(aes(y = SaKIT_ind, color = "district")) +
  ggtitle("Saturday") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        strip.text.y = element_blank()) +
  labs(x = "Time of day") +
  facet_grid(as.factor(season) ~ .,
             switch = "y")

# Sonntag
sonntagGraph <- ggplot(
  data = compare_all,
  aes(x = Time)) +
  geom_line(aes(y = SoH0_ind, color = "H0"), alpha = 0.4) +
  geom_line(aes(y = SoG1_ind, color = "G1"), alpha = 0.4) +
  geom_line(aes(y = SoG5_ind, color = "G5"), alpha = 0.4) +
  geom_line(aes(y = SoKIT_ind, color = "district")) +
  ggtitle("Sunday") +
  theme_bw() +
  theme(legend.title = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        strip.text.y = element_blank()) +
  labs(x = "time of day") +
  facet_grid(as.factor(season) ~ .,
             switch = "y")

ggarrange(werktagsGraph, samstagGraph, sonntagGraph,
          ncol = 3,
          nrow = 1,
          widths = c(1.5, 1.4, 1.8))

ggsave("./graphs/BDEW_KIT_comparison.png",
       width = 25,
       height = 8,
       units = "cm",
       dpi = 320)
```

### median

repeating the previous steps with median instead of mean to check on outliers

```{r median}
# create matrix
compare_median <- matrix(data = NA,
                     ncol = 14,
                     nrow = 3*24)
# fill matrix
colnames(compare_median) <- c("Time", "Season",
                          "MoFrKIT", "SaKIT", "SoKIT",
                          "MoFrH0", "SaH0", "SoH0",
                          "MoFrG1", "SaG1", "SoG1",
                          "MoFrG5", "SaG5", "SoG5")
compare_median[,1] <- rep(seq(0,23,1), 3)
compare_median[1:24,2] <- rep("Winter", 24)
compare_median[25:48,2] <- rep("Sommer", 24)
compare_median[49:72,2] <- rep("Uebergangszeit", 24)

# fill with KIT data
daytypes <- c("MoFr", "Sa", "So")
for(j in 1:max(data$BDEW_week)) {
  # winter
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Winter" & data$BDEW_week == j, "MGH"]
    compare_median[i + 1, paste0(daytypes[j], "KIT")] <-
      median(result[["MGH"]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Summer" & data$BDEW_week == j, "MGH"]
    compare_median[i + 25, paste0(daytypes[j], "KIT")] <-
      median(result[["MGH"]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      data[data$hour == i & data$BDEW_Season == "Uebergang" & data$BDEW_week == j, "MGH"]
    compare_median[i + 49, paste0(daytypes[j], "KIT")] <-
      median(result[["MGH"]], na.rm = TRUE)
  }
}

# fill with BDEW data
  # H0
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("Wi", daytypes[j])]
    compare_median[i + 1, paste0(daytypes[j], "H0")] <-
      median(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("So", daytypes[j])]
    compare_median[i + 25, paste0(daytypes[j], "H0")] <-
      median(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_H0[BDEW_H0$hour == i, paste0("Ueber", daytypes[j])]
    compare_median[i + 49, paste0(daytypes[j], "H0")] <-
      median(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}
  # G1
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("Wi", daytypes[j])]
    compare_median[i + 1, paste0(daytypes[j], "G1")] <-
      median(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("So", daytypes[j])]
    compare_median[i + 25, paste0(daytypes[j], "G1")] <-
      median(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_G1[BDEW_G1$hour == i, paste0("Ueber", daytypes[j])]
    compare_median[i + 49, paste0(daytypes[j], "G1")] <-
      median(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}
  # G5
for(j in 1:length(daytypes)) {
  # winter
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("Wi", daytypes[j])]
    compare_median[i + 1, paste0(daytypes[j], "G5")] <-
      median(result[[paste0("Wi", daytypes[j])]], na.rm = TRUE)
  }
  # summer
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("So", daytypes[j])]
    compare_median[i + 25, paste0(daytypes[j], "G5")] <-
      median(result[[paste0("So", daytypes[j])]], na.rm = TRUE)
  }
  # übergangszeit
  for (i in 0:23) {
    result <-
      BDEW_G5[BDEW_G5$hour == i, paste0("Ueber", daytypes[j])]
    compare_median[i + 49, paste0(daytypes[j], "G5")] <-
      median(result[[paste0("Ueber", daytypes[j])]], na.rm = TRUE)
  }
}

# turn into data frame to use in ggplot
compare_median <- as.data.frame(compare_median)
for (i in 1:ncol(compare_median)){
  # skip for season column
  if(i == 2)
    next
  else
    compare_median[,i] <- as.numeric(compare_median[,i])
}

# create sub data frames
compare_all_median <- rbind(
  scaledSeason(compare_median[compare_median$Season == "Winter",-2]),
  scaledSeason(compare_median[compare_median$Season == "Sommer",-2]),
  scaledSeason(compare_median[compare_median$Season == "Uebergangszeit",-2])
)
compare_all_median$season <- compare_median$Season

# test for differences
t.test(compare_all_median$MoFrKIT_ind, compare_all_median$MoFrH0_ind)
t.test(compare_all_median$MoFrKIT_ind, compare_all_median$MoFrG1_ind)
t.test(compare_all_median$MoFrKIT_ind, compare_all_median$MoFrG5_ind)
```

### t-test

perform t-test on difference of KIT data.

Columns have to be sticked together as vector to be fully utilised in t-test.

```{r t-test}
# create two vectors
KIT_mean <- as.vector(cbind(
  compare_all[, 'MoFrKIT_ind'],
  compare_all[, 'SaKIT_ind'],
  compare_all[, 'SoKIT_ind']
))
KIT_median <- as.vector(cbind(
  compare_all_median[, 'MoFrKIT_ind'],
  compare_all_median[, 'SaKIT_ind'],
  compare_all_median[, 'SoKIT_ind']
))
# perform test
t.test(KIT_median, KIT_mean)
```

p-value of 1 results thus the H0 has to be accepted. Thus the mean difference is 0 and can be seen as negligible.

# time series

checking if the time series is stationary or not. Using Augmented Dickey Fuller Test on all raw data time series for each building.

```{r TS_properties}
# FZI
adf.test(na.omit(data$FZI))
# MGH
adf.test(na.omit(data$MGH))
# Hoepfner
adf.test(na.omit(data$Hoepfner))
```

For all tested time series the ADF results in rejecting the H0 for all common significance levels and thus all data can be classified as stationary.

# testfield

```{r test}
# standardisation
j = 5
result <-
    vector(mode = "numeric", length = nrow(compare_median))
for (j in 3:ncol(compare_median)) {
  for (i in 1:nrow(compare_median)) {
    result[i] <-
      (compare_median[i, j] - mean(compare_median[, j], na.rm = TRUE)) / sd(compare_median[, j], na.rm = TRUE)
  }
}
```


# notizen

mehrere Plots ineinander für vergleich von BDEW & unserer Lastgänge
drei Graphen untereinander für Sommer, Winter & Übergangszeit
für H0, H1 & sonstige Lastgänge

statistische MEtriken bei Clustern
  - auch gleiche Kategorien wie bei Durschnittsberechnung
  
  - vergleich zwischen den gewerken Haushalt genuaigkeit gegen Gewerbe genauigkeit oder so...
  
  - story für quartiers gedanken mit reinbringen -> vergleiche BDEW theorie & reales quartier
  
  powerpoint mit allen Graphen
  
  BDEW Logik folgen für anfängliche Vergleiche.
  