---
title: "clustering"
author: "Jan Besler"
date: "`r Sys.Date()`"
output: html_document
---

# libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(tidyverse)
library(lubridate)
library(cluster)
library(ggplot2)
library(factoextra)
library(clusterCrit)
library(dtwclust)
```

utilising Taken's Embedding Theorem R

1.  grouping the data in daily/weekly/monthly sets
2.  draw diagram of clusters
3.  fine tune the individual clusters
4.  try to connect all data sets and run one big cluster

# data import

```{r data import}
set.seed(42)

data_wide <- read_csv("./data/data_wide.csv")

# remove days in lockdown
  # 1st lockdown 22.03.2020 - 04.05.2020
data_wide <- data_wide[!(data_wide[["date"]] >= "2020-03-22" & data_wide[["date"]] <= "2020-05-04"),]
  # 2nd lockdown 16.12.2020 - 08.05.2021
data_wide <- data_wide[!(data_wide[["date"]] >= "2020-12-16" & data_wide[["date"]] <= "2021-05-08"),]

# split data
MGH_wide <- data_wide[data_wide$location == "MGH", 2:97]
FZI_wide <- data_wide[data_wide$location == "FZI", 2:97]
Hoepfner_wide <- data_wide[data_wide$location == "Hoepfner", 2:97]
TeFak_wide <- data_wide[data_wide$location == "TechnologieFabrik", 2:97]

# scale each data set individually  - scaling only works column wise, hence transpositioning twice
data_standardised <- na.omit(rbind(
  t(scale(t(MGH_wide))),
  t(scale(t(FZI_wide))),
  t(scale(t(Hoepfner_wide))),
  t(scale(t(TeFak_wide)))
  ))
write_csv(as.data.frame(data_standardised),
          "./data/data_standardised.csv")
write_csv(data_wide,
          "./data/data_wide.csv")
```

# optimal K

### ellbow

```{r elbow, eval=FALSE}
n_clust <- 1:12
# calculate area of clusters
wss <- map_dbl(n_clust, ~{kmeans(select(data_wide, -date, -location), ., nstart=50,iter.max = 15 )$tot.withinss})
  # store results as data frame
elbow_df <- as.data.frame(cbind("n_clust" = n_clust, "wss" = wss))
  # visualize results
ggplot(elbow_df) +
  geom_line(aes(y = wss, x = n_clust)) +
  labs(x = "number of clusters", y = "WSS") +
  theme_minimal()
```

5 centers looks like it is the furthest away from the line from 1 to 24

### silhouette

pre built functions are used, since there are no easy from scratch manuals except the source code of the packages.

```{r silhouette, eval=FALSE}
silhouette_function <- function(data){
# define silhouette function
silhouette_score <- function(k, data){
  sil <- silhouette(kmeans(data, centers = k, nstart=25)$cluster,
                    dist(data))
  mean(sil[,3])
}
# apply function to every hour
avg_sil <- vector(mode = "numeric", length = length(n_clust) - 1)
for(i in 2:length(n_clust)){
  avg_sil[i] <- silhouette_score(i, data)
}
# create df to use in ggplot
avg_sil_df <- as.data.frame(avg_sil)
avg_sil_df <- cbind(avg_sil_df, n_clust)
return(avg_sil_df)
}


avg_sil_df <- silhouette_function(MGH_wide)


# visualize results
ggplot(avg_sil_df) +
  geom_line(aes(y = avg_sil, x = n_clust)) +
  geom_vline(xintercept = avg_sil_df[avg_sil_df$avg_sil == max(avg_sil_df$avg_sil), 'n_clust'],
             linetype = "dashed") +
  labs(x = "number of clusters", y = "average silhouette score") +
  theme_minimal()

avg_sil_df[avg_sil_df$avg_sil == max(avg_sil_df$avg_sil), 'n_clust']

```

### gap statistics

Again using a pre-built function.

```{r gap, eval=FALSE}
GapStats <- clusGap(x = MGH_wide,
        FUNcluster = kmeans,
        nstart = 25,
        K.max = length(n_clust),
        B = 20,
        iter.max = 20,
        verbose = TRUE)
fviz_gap_stat(GapStats)
```

# clustering functions

### k-means euclidean

```{r k-means}
k_means_euclidean <- function(data, k_low, k_high) {
  k_means_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(k_means_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  k_means_evaluation[, 1] <- c("Silhouette",
                               "Calinski_Harabasz",
                               "Davies_Bouldin",
                               "Dunn")
  # cluster assignments
  k_means_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(k_means_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in k_low:k_high) {
    # run clustering
    k_means <- tsclust(
      data,
      k = i,
      type = "partitional",      # partition around medoids
      preproc = zscore,      # z-normalisation
      distance = "L2",      # shape based distance
      centroid = "mean",      # partition around mediods
      seed = 42
    )
    # evaluate clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      k_means@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {
      k_means_evaluation[j, i] <- evaluation[j]
    }
    k_means_cluster[, i - 1] <- k_means@cluster
  }
  k_means <- list("cluster" = k_means_cluster, "evaluation" = k_means_evaluation)
  return(k_means)
}
```

### k-mediods euclidean

```{r k_mediods}
k_mediod_euclidean <- function(data, k_low, k_high) {
  k_mediod_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(k_mediod_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  k_mediod_evaluation[, 1] <- c("Silhouette",
                                "Calinski_Harabasz",
                                "Davies_Bouldin",
                                "Dunn")
  # cluster assignments
  k_mediod_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(k_mediod_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in k_low:k_high) {
    # run clustering
    k_mediod <- tsclust(
      data,
      k = i,
      type = "partitional",      # partition around medoids
      preproc = zscore,      # z-normalisation
      distance = "L2",      # euclidean distance
      centroid = "pam",      # partition around mediods
      seed = 42
    )
    # evaluate clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      k_mediod@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {k_mediod_evaluation[j, i] <- evaluation[j]}
    k_mediod_cluster[, i - 1] <- k_mediod@cluster
  }
  k_mediod <- list("cluster" = k_mediod_cluster, "evaluation" = k_mediod_evaluation)
  return(k_mediod)
}
```

### c-means euclidean

use the wide data set, since it is required that the data is a matrix with variables as columns and observations as rows.

Set `m = 2` as recommended by *Hathaway and Bezdek 2001*

```{r c-means}
c_means_euclidean <- function(data, k_low, k_high) {
  # internal evaluation
  c_means_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(c_means_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  c_means_evaluation[, 1] <- c("Silhouette",
                               "Calinski_Harabasz",
                               "Davies_Bouldin",
                               "Dunn")
  # cluster assignments
  c_means_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(c_means_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in k_low:k_high) {
    # run clustering
    c_means <- tsclust(
      data,
      k = i,
      type = "fuzzy",      # fuzzy clustering
      preproc = zscore,      # z-normalisation
      distance = "L2",      # euclidean distance
      centroid = "fcmdd",      # partition around fuzzy mediods
      seed = 42
    )
    # evaluate clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      c_means@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {c_means_evaluation[j, i] <- evaluation[j]}
    c_means_cluster[, i - 1] <- c_means@cluster
  }
  c_means <- list("cluster" = c_means_cluster, "evaluation" = c_means_evaluation)
  return(c_means)
}
```

### k-shape dtw

using {dtwclust} for the distance measurements dynamic time warping is utilised

```{r k_dtw}
k_shape <- function(data, k_low, k_high) {
  k_dtw_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(k_dtw_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  k_dtw_evaluation[, 1] <- c("Silhouette",
                             "Calinski_Harabasz",
                             "Davies_Bouldin",
                             "Dunn")
  # cluster assignments
  k_dtw_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(k_dtw_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in 2:5) {
    # run clustering
    k_dtw <- tsclust(
      data,
      k = i,
      type = "partitional",      # partition around medoids
      preproc = zscore,      # z-normalisation
      distance = "sbd",      # shape based distance
      centroid = "shape",      # shape averaging
      seed = 42
    )
    # evaluate clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      k_dtw@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {k_dtw_evaluation[j, i] <- evaluation[j]}
    k_dtw_cluster[, i - 1] <- k_dtw@cluster
  }
  k_shape <- list("cluster" = k_dtw_cluster, "evaluation" = k_dtw_evaluation)
  return(k_shape)
}
```

### c-means dtw

```{r c_dtw, eval=T}
c_means_dtw <- function(data, k_low, k_high) {
  c_dtw_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(c_dtw_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  c_dtw_evaluation[, 1] <- c("Silhouette",
                             "Calinski_Harabasz",
                             "Davies_Bouldin",
                             "Dunn")
  # cluster assignments
  c_dtw_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(c_dtw_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in 2:5) {
    c_dtw <- tsclust(
      data,
      k = i,
      type = "fuzzy",      # fuzzy clustering
      preproc = zscore,      # z-normalisation
      distance = "dtw",      # standard dynamic time warping
      centroid = "fcmdd",      # fuzzy suitable for vectors of different length
      seed = 42,
      trace = TRUE,
      control = fuzzy_control(fuzziness = 2,
                              iter.max = 10L)
    )
    # evaluation of clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      c_dtw@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {c_dtw_evaluation[j, i] <- evaluation[j]}
    c_dtw_cluster[, i - 1] <- c_dtw@cluster
  }
  c_means <- list("cluster" = c_dtw_cluster, "evaluation" = c_dtw_evaluation)
  return(c_means)
}
```

### dtw cluster

```{r dtw_clustering, eval=T}
dtw_cluster <- function(data, k_low, k_high) {
  dtw_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 5,
      nrow = 4
    ))
  colnames(dtw_evaluation) <- c("evaluation method", "k = 2", "k = 3", "k = 4", "k = 5")
  dtw_evaluation[, 1] <- c("Silhouette",
                           "Calinski_Harabasz",
                           "Davies_Bouldin",
                           "Dunn")
  # cluster assignments
  dtw_cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 4,
      nrow = nrow(data)
    ))
  colnames(dtw_cluster) <- c("k = 2", "k = 3", "k = 4", "k = 5")
  
  for (i in 2:5) {
    dtw <- tsclust(
      data,
      k = i,
      type = "partitional",      # partition around centroids
      preproc = zscore,      # z-normalisation
      distance = "dtw",      # euclidean distance
      centroid = "sdtw_cent",      # soft-DTW centroids
      seed = 42,
      trace = TRUE
    )
    # evaluate clustering - internal
    evaluation <- intCriteria(
      as.matrix(data),
      dtw@cluster,
      c("Silhouette",
        "Calinski_Harabasz",
        "Davies_Bouldin",
        "Dunn")
    )
    for (j in 1:length(evaluation)) {dtw_evaluation[j, i] <- evaluation[j]}
    dtw_cluster[, i - 1] <- dtw@cluster
  }
  dtw <- list("cluster" = dtw_cluster, "evaluation" = dtw_evaluation)
  return(dtw)
}
```

### BDEW comparison

```{r BDEW_comparison}
BDEW_comparison <- function(data) {
  BDEW_evaluation <-
    as.data.frame(matrix(
      data = NA,
      ncol = 7,
      nrow = 4
    ))
  colnames(BDEW_evaluation) <-
    c(
      "evaluation method",
      "k-means",
      "k-mediod",
      "c-means eucl",
      "k-shape",
      "c-means dtw",
      "dtw"
    )
  BDEW_evaluation[, 1] <- c("Silhouette",
                            "Calinski_Harabasz",
                            "Davies_Bouldin",
                            "Dunn")
  # cluster assignments
  cluster <-
    as.data.frame(matrix(
      data = NA,
      ncol = 6,
      nrow = nrow(data)
    ))
  colnames(cluster) <-
    c("k-means",
      "k-mediod",
      "c-means eucl",
      "k-shape",
      "c-means dtw",
      "dtw")
  
  # k-means
  k_means <- tsclust(
    data,
    k = 9,
    type = "partitional",
    # partition around medoids
    preproc = zscore,
    # z-normalisation
    distance = "L2",
    # shape based distance
    centroid = "mean",
    # partition around mediods
    seed = 42
  )
  evaluation <- intCriteria(
    as.matrix(data),
    k_means@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "k-means"] <- evaluation[j]
  }
  cluster[, "k-means"] <- k_means@cluster
  
  # k-mediod
  k_mediod <- tsclust(
    data,
    k = 9,
    type = "partitional",
    # partition around medoids
    preproc = zscore,
    # z-normalisation
    distance = "L2",
    # euclidean distance
    centroid = "pam",
    # partition around mediods
    seed = 42
  )
  evaluation <- intCriteria(
    as.matrix(data),
    k_mediod@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "k-mediod"] <- evaluation[j]
  }
  cluster[, "k-mediod"] <- k_mediod@cluster
  
  # c-means eucl
  c_means <- tsclust(
    data,
    k = 9,
    type = "fuzzy",
    # fuzzy clustering
    preproc = zscore,
    # z-normalisation
    distance = "L2",
    # euclidean distance
    centroid = "fcmdd",
    # partition around fuzzy mediods
    seed = 42
  )
  # evaluate clustering - internal
  evaluation <- intCriteria(
    as.matrix(data),
    c_means@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "c-means eucl"] <- evaluation[j]
  }
  cluster[, "c-means eucl"] <- c_means@cluster
  
  # k-shape
  k_dtw <- tsclust(
    data,
    k = 9,
    type = "partitional",
    # partition around medoids
    preproc = zscore,
    # z-normalisation
    distance = "sbd",
    # shape based distance
    centroid = "shape",
    # shape averaging
    seed = 42
  )
  # evaluate clustering - internal
  evaluation <- intCriteria(
    as.matrix(data),
    k_dtw@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "k-shape"] <- evaluation[j]
  }
  cluster[, "k-shape"] <- k_dtw@cluster
  
  # c-means dtw
  c_dtw <- tsclust(
    data,
    k = 9,
    type = "fuzzy",
    # fuzzy clustering
    preproc = zscore,
    # z-normalisation
    distance = "dtw",
    # standard dynamic time warping
    centroid = "fcmdd",
    # fuzzy suitable for vectors of different length
    seed = 42,
    trace = TRUE,
    control = fuzzy_control(fuzziness = 2,
                            iter.max = 10L)
  )
  # evaluation of clustering - internal
  evaluation <- intCriteria(
    as.matrix(data),
    c_dtw@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "c-means dtw"] <- evaluation[j]
  }
  cluster[, "c-means dtw"] <- c_dtw@cluster
  
  # dtw
  dtw <- tsclust(
    data,
    k = 9,
    type = "partitional",
    # partition around centroids
    preproc = zscore,
    # z-normalisation
    distance = "dtw",
    # euclidean distance
    centroid = "sdtw_cent",
    # soft-DTW centroids
    seed = 42,
    trace = TRUE
  )
  # evaluate clustering - internal
  evaluation <- intCriteria(
    as.matrix(data),
    dtw@cluster,
    c("Silhouette",
      "Calinski_Harabasz",
      "Davies_Bouldin",
      "Dunn")
  )
  for (j in 1:length(evaluation)) {
    BDEW_evaluation[j, "dtw"] <- evaluation[j]
  }
  cluster[, "dtw"] <- dtw@cluster
  
  
  BDEW_df <-
    list("cluster" = cluster, "evaluation" = BDEW_evaluation)
  return(BDEW_df)
}
```

### centres

```{r centres}
centres_k_means <- function(data, opt_k) {
  for (i in opt_k) {
    k_means <- tsclust(
      data,
      k = i,
      type = "partitional",     # partition around medoids
      preproc = zscore,      # z-normalisation
      distance = "L2",      # shape based distance
      centroid = "mean",      # partition around mediods
      seed = 42
    )
    centres <- matrix(data = NA,
                      nrow = 96,
                      ncol = i)
    for (j in 1:i) {
      centres[, j] <- k_means@centroids[[j]]
    }
  }
  return(centres)
}

centres_c_means <- function(data, opt_k) {
  for (i in opt_k) {
    c_means <- tsclust(
      data,
      k = i,
      type = "fuzzy",      # fuzzy clustering
      preproc = zscore,      # z-normalisation
      distance = "L2",      # euclidean distance
      centroid = "fcmdd",      # partition around fuzzy mediods
      seed = 42
    )
    centres <- matrix(data = NA,
                      nrow = 96,
                      ncol = i)
    for (j in 1:i) {
      centres[, j] <- c_means@centroids[[j]]
    }
  }
  return(centres)
}
```


# whole data set

### clustering

```{r whole_data, eval=FALSE}
k_means_whole <- k_means_euclidean(data_standardised, 2, 9)

c_means_whole <- c_means_euclidean(data_standardised, 2, 9)

k_mediod_whole <- k_mediod_euclidean(data_standardised, 2, 9)

# DO NOT RUN - takes ~6 hours from here on
c_means_dtw_whole <- c_means_dtw(data_standardised, 2, 9)

k_shape_whole <- k_shape(data_standardised, 2, 9)

dtw_whole <- dtw_cluster(data_standardised, 2, 9)

BDEW_whole <- BDEW_comparison(data_standardised)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_whole, eval=FALSE}
# store relevant values in data frame
cluster_df <- as.data.frame(matrix(data = NA, ncol = 6, nrow = nrow(data_standardised)))
colnames(cluster_df) <- c("k-means", "k-mediod", "c-means", "c-means-dtw", "k-shape", "dtw")

cluster_df$`k-means` <- k_means_whole$cluster$`k = 2`
cluster_df$`k-mediod` <- k_mediod_whole$cluster$`k = 2`
cluster_df$`c-means` <- c_means_whole$cluster$`k = 2`
cluster_df$`c-means-dtw` <-c_means_dtw_whole$cluster$`k = 2`
cluster_df$`k-shape` <- k_shape_whole$cluster$`k = 2`
cluster_df$dtw <- dtw_whole$cluster$`k = 2`

write_csv(
  cluster_df,
  "./data/cluster_whole.csv"
)

write_csv(
  as.data.frame(centres_k_means(data_standardised, 2)),
  "./data/centre_whole.csv"
)
```


# MGH data set

### clustering

```{r MGH}
k_means_MGH <- k_means_euclidean(MGH_wide, 2, 9)

c_means_MGH <- c_means_euclidean(MGH_wide, 2, 9)

k_mediod_MGH <- k_mediod_euclidean(MGH_wide, 2, 9)

# DO NOT RUN - takes ~6 hours from here on
c_means_dtw_MGH <- c_means_dtw(MGH_wide, 2, 9)

k_shape_MGH <- k_shape(MGH_wide, 2, 9)

dtw_MGH <- dtw_cluster(MGH_wide, 2, 9)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_MGH, eval=FALSE}
# store relevant values in data frame
cluster_df <- as.data.frame(matrix(data = NA, ncol = 6, nrow = nrow(MGH_wide)))
colnames(cluster_df) <- c("k-means", "k-mediod", "c-means", "c-means-dtw", "k-shape", "dtw")

cluster_df$`k-means` <- k_means_MGH$cluster$`k = 4`
cluster_df$`k-mediod` <- k_mediod_MGH$cluster$`k = 3`
cluster_df$`c-means` <- c_means_MGH$cluster$`k = 2`
cluster_df$`c-means-dtw` <- c_means_dtw_MGH$cluster$`k = 2`
cluster_df$`k-shape` <- k_shape_MGH$cluster$`k = 5`
cluster_df$dtw <- dtw_MGH$cluster$`k = 3`

write_csv(
  cluster_df,
  "./data/cluster_MGH.csv"
)

write_csv(
  as.data.frame(centres_k_means(MGH_wide, 4)),
  "./data/centre_MGH.csv"
)
```


# FZI data set

### clustering

```{r FZI}
k_means_FZI <- k_means_euclidean(FZI_wide, 2, 9)

c_means_FZI <- c_means_euclidean(FZI_wide, 2, 9)

k_mediod_FZI <- k_mediod_euclidean(FZI_wide, 2, 9)

# DO NOT RUN - takes ~6 hours from here on
c_means_dtw_FZI <- c_means_dtw(FZI_wide, 2, 9)

k_shape_FZI <- k_shape(FZI_wide, 2, 9)

dtw_FZI <- dtw_cluster(FZI_wide, 2, 9)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_FZI, eval=FALSE}
# store relevant values in data frame
cluster_df <- as.data.frame(matrix(data = NA, ncol = 6, nrow = nrow(FZI_wide)))
colnames(cluster_df) <- c("k-means", "k-mediod", "c-means", "c-means-dtw", "k-shape", "dtw")

cluster_df$`k-means` <- k_means_FZI$cluster$`k = 2`
cluster_df$`k-mediod` <- k_mediod_FZI$cluster$`k = 2`
cluster_df$`c-means` <- c_means_FZI$cluster$`k = 2`
cluster_df$`c-means-dtw` <- c_means_dtw_FZI$cluster$`k = 3`
cluster_df$`k-shape` <- k_shape_FZI$cluster$`k = 4`
cluster_df$dtw <- dtw_FZI$cluster$`k = 2`

write_csv(
  cluster_df,
  "./data/cluster_FZI.csv"
)

write_csv(
  as.data.frame(centres_k_means(FZI_wide, 2)),
  "./data/centre_FZI.csv"
)
```

# Hoepfner data set

### clustering

```{r Hoepfner}
k_means_Hoepfner <- k_means_euclidean(Hoepfner_wide, 2, 9)

c_means_Hoepfner <- c_means_euclidean(Hoepfner_wide, 2, 9)

k_mediod_Hoepfner <- k_mediod_euclidean(Hoepfner_wide, 2, 9)

# DO NOT RUN - takes ~6 hours from here on
c_means_dtw_Hoepfner <- c_means_dtw(Hoepfner_wide, 2, 9)

k_shape_Hoepfner <- k_shape(Hoepfner_wide, 2, 9)

dtw_Hoepfner <- dtw_cluster(Hoepfner_wide, 2, 9)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_Hoepfner, eval=FALSE}
# store relevant values in data frame
cluster_df <- as.data.frame(matrix(data = NA, ncol = 6, nrow = nrow(Hoepfner_wide)))
colnames(cluster_df) <- c("k-means", "k-mediod", "c-means", "c-means-dtw", "k-shape", "dtw")

cluster_df$`k-means` <- k_means_Hoepfner$cluster$`k = 2`
cluster_df$`k-mediod` <- k_mediod_Hoepfner$cluster$`k = 2`
cluster_df$`c-means` <- c_means_Hoepfner$cluster$`k = 3`
cluster_df$`c-means-dtw` <-c_means_dtw_Hoepfner$cluster$`k = 4`
cluster_df$`k-shape` <- k_shape_Hoepfner$cluster$`k = 3`
cluster_df$dtw <- dtw_Hoepfner$cluster$`k = 2`

write_csv(
  cluster_df,
  "./data/cluster_Hoepfner.csv"
)

write_csv(
  as.data.frame(centres_k_means(Hoepfner_wide, 2)),
  "./data/centre_Hoepfner.csv"
)
```

# TeFak data set

### clustering

```{r TeFak}
k_means_TeFak <- k_means_euclidean(TeFak_wide, 2, 9)

c_means_TeFak <- c_means_euclidean(TeFak_wide, 2, 9)

k_mediod_TeFak <- k_mediod_euclidean(TeFak_wide, 2, 9)

# DO NOT RUN - takes ~6 hours from here on
c_means_dtw_TeFak <- c_means_dtw(TeFak_wide, 2, 9)

k_shape_TeFak <- k_shape(TeFak_wide, 2, 9)

dtw_TeFak <- dtw_cluster(TeFak_wide, 2, 9)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_TeFak, eval=FALSE}
# store relevant values in data frame
cluster_df <- as.data.frame(matrix(data = NA, ncol = 6, nrow = nrow(TeFak_wide)))
colnames(cluster_df) <- c("k-means", "k-mediod", "c-means", "c-means-dtw", "k-shape", "dtw")

cluster_df$`k-means` <- k_means_TeFak$cluster$`k = 2`
cluster_df$`k-mediod` <- k_mediod_TeFak$cluster$`k = 2`
cluster_df$`c-means` <- c_means_TeFak$cluster$`k = 2`
cluster_df$`c-means-dtw` <- c_means_dtw_TeFak$cluster$`k = 3`
cluster_df$`k-shape` <- k_shape_TeFak$cluster$`k = 2`
cluster_df$dtw <- dtw_TeFak$cluster$`k = 2`

write_csv(
  cluster_df,
  "./data/cluster_TeFak.csv"
)

write_csv(
  as.data.frame(centres_c_means(TeFak_wide, 2)),
  "./data/centre_TeFak.csv"
)
```

# BDEW comparison

```{r BDEW_all}
#BDEW_whole <- BDEW_comparison(data_standardised)

BDEW_MGH <- BDEW_comparison(MGH_wide)

BDEW_FZI <- BDEW_comparison(FZI_wide)

BDEW_Hoepfner <- BDEW_comparison(Hoepfner_wide)

BDEW_TeFak <- BDEW_comparison(TeFak_wide)
```

### cluster assignment

to add the cluster information to the data, it is stored in a separate data frame to be called on later on again.

```{r cluster_assignment_BDEW, eval=FALSE}
# store relevant values in data frame
cluster_df <- vector(mode = "list", length = 4)
names(cluster_df) <- c("FZI", "Hoepfner", "MGH", "TeFak")

cluster_df$FZI <- BDEW_FZI$cluster$`k-means`
cluster_df$Hoepfner <- BDEW_Hoepfner$cluster$`k-means`
cluster_df$MGH <- BDEW_MGH$cluster$`k-means`
cluster_df$TeFak <- BDEW_TeFak$cluster$`k-shape`

capture.output(
  cluster_df,
  file = "./data/cluster_BDEW.csv"
)
```

# test

```{r test, eval=FALSE}
k_means_center <- as.data.frame(k_means@centroids, col.names = colnames(k_means_cluster))
# comparison - external
  # k = 2
extCriteria(
  k_dtw_cluster[,1],
  k_mediod_cluster[,1],
  c("Rand",
    "Russel_Rao")
)






```

