---
title: "Cluster Assignment"
author: "Jan Besler"
date: "`r Sys.Date()`"
output: html_document
---

# libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(tidyverse)
library(data.table)
library(lubridate)
library(cluster)
library(ggplot2)
library(ggExtra)
library(ggpubr)
library(factoextra)
library(clusterCrit)
library(dtwclust)
library(scales)
```

utilising Taken's Embedding Theorem R

1.  grouping the data in daily/weekly/monthly sets
2.  draw diagram of clusters
3.  fine tune the individual clusters
4.  try to connect all data sets and run one big cluster

# data import

```{r data import}
data_wide <- read_csv("./data/data_wide.csv")
data_standardised <- read_csv("./data/data_standardised.csv")
cluster_whole <- read_csv("./data/cluster_whole.csv")

# cluster matrices
MGH_cluster <- read_csv("./data/cluster_MGH.csv")
FZI_cluster <- read_csv("./data/cluster_FZI.csv")
Hoepfner_cluster <- read_csv("./data/cluster_Hoepfner.csv")
TeFak_cluster <- read_csv("./data/cluster_TeFak.csv")
BDEW_cluster <- read_csv("./data/cluster_BDEW.csv")

# centre matrices
MGH_centre <- read_csv("./data/centre_MGH.csv")
FZI_centre <- read_csv("./data/centre_FZI.csv")
Hoepfner_centre <- read_csv("./data/centre_Hoepfner.csv")
TeFak_centre <- read_csv("./data/centre_TeFak.csv")
```

# transform

create full data set with cluster and meta information & use descriptive statistics to find properties of clusters.

```{r transform data}
meta_evaluation <- function(data, cluster_data) {
  # add cluster information to wide data set
  data_wide <- data %>%
    mutate(cluster = cluster_data)
  
  # change back to long format
  data_long <- data_wide %>%
    pivot_longer(
      cols = c(-date,-cluster,-location),
      names_to = "time",
      values_to = "Verbrauch"
    )
  # change date column type
  data_long$date <- dmy(data_long$date)
  
  # add meta information
  setDT(data_long)
  # weekdays
  data_long <- data_long[, dayOfWeek := weekdays(date, abbreviate = TRUE)]
  # calendar week
  data_long <- data_long[, calendarWeek := isoweek(date)]
  # month
  data_long <- data_long[, month := month(date)]
  # BDEW weekend
  data_long <- data_long[, weekend :=
                          ifelse(dayOfWeek == "Sun",
                                  "Sunday",
                                  ifelse(dayOfWeek == "Sat", "Saturday", "working day"))]
  # variable for BDEW-season
  data_long <- data_long[, BDEWSeason :=
                          ifelse(month >= 12 | month <= 2,
                                  "Winter",
                                  ifelse(month >= 6 & month <= 9, "Summer", "Transition"))]
  # hour variable
  data_long <- data_long[, hour := as.numeric(substr(time, 1, 2))]
  
  # reorder column for better looking data frame
  setcolorder(
    data_long,
    c(
      "date",
      "location",
      "cluster",
      "Verbrauch",
      "BDEWSeason",
      "month",
      "calendarWeek",
      "dayOfWeek",
      "weekend",
      "hour",
      "time"
    )
  )
  
  # evaluation
  # location <- matrix(data = NA,
  #                    ncol = length(unique(data_long$cluster)),
  #                    nrow = length(unique(data_long$location)))
  # month <- matrix(data = NA,
  #                 ncol = length(unique(data_long$cluster)),
  #                 nrow = length(unique(data_long$month)))
  # calendarweek <- matrix(data = NA,
  #                        ncol = length(unique(data_long$cluster)),
  #                        nrow = length(unique(data_long$calendarWeek)))
  # weekday <- matrix(data = NA,
  #                   ncol = length(unique(data_long$cluster)),
  #                   nrow = length(unique(data_long$dayOfWeek)))
  weekend <- matrix(data = NA,
                    ncol = length(unique(data_long$cluster)),
                    nrow = length(unique(data_long$weekend)))
  BDEWSeason <- matrix(data = NA,
                       ncol = length(unique(data_long$cluster)),
                       nrow = length(unique(data_long$BDEWSeason)))
  
  # fill tables
  for (i in 1:length(unique(data_long$cluster))) {
    df <- data_long[data_long[, cluster == i]]
    # location
#    location[, i] <-
#      table(factor(df$location, levels = c("MGH", "FZI", "Hopefner", "TechnologieFabrik"))) /
#      table(data_long$location)
#    rownames(location) <-
#      names(table(factor(df$location, levels = c("MGH", "FZI", "Hopefner", "TechnologieFabrik"))))
    # month
    # month[, i] <-
    #   table(factor(df$month, levels = 1:12)) /
    #   table(data_long$month)
    # rownames(month) <- names(table(factor(df$month, levels = 1:12)))
    # # calenderweek
    # calendarweek[, i] <-
    #   table(factor(df$calendarWeek, levels = 1:53)) /
    #   table(data_long$calendarWeek)
    # rownames(calendarweek) <- names(table(factor(df$calendarWeek, levels = 1:53)))
    # # day of the week
    # weekday[, i] <-
    #   table(factor(df$dayOfWeek, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) /
    #   table(data_long$dayOfWeek)
    # rownames(weekday) <-
    #   names(table(factor(df$dayOfWeek, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))))
    # weekend
    weekend[, i] <-
      table(factor(df$weekend, levels = c("Saturday", "Sunday", "working day"))) /
      table(data_long$weekend)
    rownames(weekend) <- names(table(factor(df$weekend, levels = c("Saturday", "Sunday", "working day"))))
    # BDEW-Season1
    BDEWSeason[, i] <-
      table(factor(df$BDEWSeason, levels = c("Summer", "Transition", "Winter"))) /
      table(data_long$BDEWSeason)
    rownames(BDEWSeason) <- names(table(factor(df$BDEWSeason, levels = c("Summer", "Transition", "Winter"))))
  }
  evaluate_list <- list(
#    "location" = location,
    # "month" = month,
    # "calendarweek" = calendarweek,
    # "weekday" = weekday,
    "weekend" = weekend,
    "BDEWSeason" = BDEWSeason
  )
  return(evaluate_list)
}
```

# evaluation

```{r evaluation_buildings, eval=FALSE}
MGH_eval <- meta_evaluation(
  data_wide[data_wide$location == "MGH",],
  MGH_cluster$`k-means`
)

FZI_eval <- meta_evaluation(
  data_wide[data_wide$location == "FZI",],
  FZI_cluster$`k-means`
)

Hoepfner_eval <- meta_evaluation(
  data_wide[data_wide$location == "Hoepfner",],
  Hoepfner_cluster$`k-means`
)

TeFak_eval <- meta_evaluation(
  data_wide[data_wide$location == "TechnologieFabrik",],
  TeFak_cluster$`c-means`
)
```


# visualisation

### function

```{r vis_function}
graph_area <- function(data, cluster_wide) {
  cluster_data <- cluster_wide
  data <- data %>%
    mutate(cluster = cluster_data)
  graph_area_df <- as.data.frame(matrix(
    data = NA,
    ncol = length(unique(data$cluster)) * 2,
    nrow = 96
  ))
  # left value min, right max
  for (i in 1:length(unique(data$cluster))) {
    graph_area_df[, (2 * i - 1):(2 * i)] <-
      t(data[c(which.max(rowMeans(data[data$cluster == i, -97])),
               which.min(rowMeans(data[data$cluster == i, -97]))), -97])
  }
  return(graph_area_df)
}

z_score <- function(data){
  z = (data - mean(data)) / sd(data)
  return(z)
}

cluster_df <- function(data, cluster_data) {
  # data preparation
  data_cl <- data %>% mutate(cluster = cluster_data)
  min_max <-
    matrix(data = NA,
           nrow = 96,
           ncol = length(unique(data_cl$cluster)) * 2)
  density_plot <- vector("list", length = length(unique(data_cl$cluster)))
  for (k in 1:length(unique(data_cl$cluster))) {
    data_k <- data_cl[data_cl$cluster == k, 1:96]
    # min & max values
    min_vec <- vector(mode = "numeric", length = 96)
    max_vec <- vector(mode = "numeric", length = 96)
    for (i in 1:96) {
      min_vec[i] <- min(data_k[, i])
      max_vec[i] <- max(data_k[, i])
    }
    min_max[, (2 * k - 1):(2 * k)] <- t(rbind(min_vec, max_vec))
    # density
    density_plot[[k]] <- rowMeans(data_k)
  }
  # centre
  cluster <- kmeans(
    data,
    centers = length(unique(data_cl$cluster)),
    iter.max = 25,
    nstart = 10
  )
  centre <- as.data.frame(cluster$centers)
  # time stamps
  time_stamps <- seq(from = as.POSIXct("2019-01-01", tz = "GMT"), length.out = 96, by = "15 min")
  # one data frame
  df <- as.data.frame(cbind(min_max, t(centre)))
  df$time <- time_stamps
  final_list <- list("main_graph" = df, "density" = density_plot)
  return(final_list) 
}
```

### graphs

```{r graph_data, eval=FALSE}
# FZI
FZI <- cluster_df(data_wide[data_wide$location == "FZI",2:97], FZI_cluster$`k-means`)
names(FZI$main_graph) <- c("min_vec_cl1", "max_vec_cl1",
                           "min_vec_cl2", "max_vec_cl2",
                           "cl1", "cl2", "time")
density_cl1_FZI <- as.data.frame(FZI$density[[1]])
names(density_cl1_FZI) <- c("avg")
density_cl2_FZI <- as.data.frame(FZI$density[[2]])
names(density_cl2_FZI) <- c("avg")

# MGH
MGH <- cluster_df(data_wide[data_wide$location == "MGH",2:97], MGH_cluster$`k-means`)
names(MGH$main_graph) <- c("min_vec_cl1", "max_vec_cl1",
                           "min_vec_cl2", "max_vec_cl2",
                           "min_vec_cl3", "max_vec_cl3",
                           "min_vec_cl4", "max_vec_cl4",
                           "cl1", "cl2", "cl3", "cl4", "time")
density_cl1_MGH <- as.data.frame(MGH$density[[1]])
names(density_cl1_MGH) <- c("avg")
density_cl2_MGH <- as.data.frame(MGH$density[[2]])
names(density_cl2_MGH) <- c("avg")
density_cl3_MGH <- as.data.frame(MGH$density[[3]])
names(density_cl3_MGH) <- c("avg")
density_cl4_MGH <- as.data.frame(MGH$density[[4]])
names(density_cl4_MGH) <- c("avg")

# Hoepfner
Hoepfner <- cluster_df(data_wide[data_wide$location == "Hoepfner",2:97], Hoepfner_cluster$`k-means`)
names(Hoepfner$main_graph) <- c("min_vec_cl1", "max_vec_cl1",
                           "min_vec_cl2", "max_vec_cl2",
                           "cl1", "cl2", "time")
density_cl1_Hoepfner <- as.data.frame(Hoepfner$density[[1]])
names(density_cl1_Hoepfner) <- c("avg")
density_cl2_Hoepfner <- as.data.frame(Hoepfner$density[[2]])
names(density_cl2_Hoepfner) <- c("avg")

# TeFak
TeFak <- cluster_df(data_wide[data_wide$location == "TechnologieFabrik",2:97], TeFak_cluster$`k-means`)
names(TeFak$main_graph) <- c("min_vec_cl1", "max_vec_cl1",
                           "min_vec_cl2", "max_vec_cl2",
                           "cl1", "cl2", "time")
density_cl1_TeFak <- as.data.frame(TeFak$density[[1]])
names(density_cl1_TeFak) <- c("avg")
density_cl2_TeFak <- as.data.frame(TeFak$density[[2]])
names(density_cl2_TeFak) <- c("avg")
```

##### FZI

```{r FZI_vis, eval=T}
FZI_1 <- ggplot(as.data.frame(FZI$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl1)) + # min
  geom_line(aes(y = max_vec_cl1)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl1,
    ymax = max_vec_cl1),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl1), col = "#b58900", size = 0.5) +
  # density
  geom_point(data = density_cl1_FZI,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("First Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 60000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
FZI_1 <- ggMarginal(FZI_1, type = "density", margins = "y")

FZI_2 <- ggplot(as.data.frame(FZI$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl2)) + # min
  geom_line(aes(y = max_vec_cl2)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl2,
    ymax = max_vec_cl2),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl2), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl2_FZI,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Second Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 60000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
FZI_2 <- ggMarginal(FZI_2, type = "density", margins = "y")

ggarrange(
  FZI_1, FZI_2,
  ncol = 2, nrow = 1,
  widths = c(1.3, 1.1)
)

ggsave("./graphs/FZI_cluster_profiles.png",
       dpi = 320,
       width = 16,
       height = 5,
       units = "cm")
```

##### MGH

```{r MGH_vis, eval=FALSE}
MGH_1 <- ggplot(as.data.frame(MGH$main_graph),
                aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl1)) + # min
  geom_line(aes(y = max_vec_cl1)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl1,
    ymax = max_vec_cl1),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl4), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl1_MGH,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("First Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
MGH_1 <- ggMarginal(MGH_1, type = "density", margins = "y")

MGH_2 <- ggplot(as.data.frame(MGH$main_graph),
                aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl2)) + # min
  geom_line(aes(y = max_vec_cl2)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl2,
    ymax = max_vec_cl2),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl3), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl2_MGH,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Second Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        axis.title.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
MGH_2 <- ggMarginal(MGH_2, type = "density", margins = "y")

MGH_3 <- ggplot(as.data.frame(MGH$main_graph),
                aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl3)) + # min
  geom_line(aes(y = max_vec_cl3)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl3,
    ymax = max_vec_cl3),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl2), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl3_MGH,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Third Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.ticks.x = element_blank(),
        #axis.text.x = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
MGH_3 <- ggMarginal(MGH_3, type = "density", margins = "y")

MGH_4 <- ggplot(as.data.frame(MGH$main_graph),
                aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl4)) + # min
  geom_line(aes(y = max_vec_cl4)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl4,
    ymax = max_vec_cl4),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl1), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl4_MGH,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Fourth Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        #axis.ticks.x = element_blank(),
        #axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
MGH_4 <- ggMarginal(MGH_4, type = "density", margins = "y")

ggarrange(
  MGH_1, MGH_2, MGH_3, MGH_4,
  nrow = 2, ncol = 2,
  widths = c(1.3,1.1,
             1.3,1.1)
)

ggsave("./graphs/MGH_cluster_profiles.png",
       dpi = 320,
       width = 16,
       height = 9,
       units = "cm")
```

##### Hoepfner

```{r Hoepfner_vis}
Hoepfner_1 <- ggplot(as.data.frame(Hoepfner$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl1)) + # min
  geom_line(aes(y = max_vec_cl1)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl1,
    ymax = max_vec_cl1),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl2), col = "#b58900", size = 0.5) +
  # density
  geom_point(data = density_cl1_Hoepfner,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("First Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
Hoepfner_1 <- ggMarginal(Hoepfner_1, type = "density", margins = "y")

Hoepfner_2 <- ggplot(as.data.frame(Hoepfner$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl2)) + # min
  geom_line(aes(y = max_vec_cl2)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl2,
    ymax = max_vec_cl2),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl1), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl2_Hoepfner,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Second Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 100000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
Hoepfner_2 <- ggMarginal(Hoepfner_2, type = "density", margins = "y")

ggarrange(
  Hoepfner_1, Hoepfner_2,
  ncol = 2, nrow = 1,
  widths = c(1.3, 1.1)
)

ggsave("./graphs/Hoepfner_cluster_profiles.png",
       dpi = 320,
       width = 16,
       height = 5,
       units = "cm")
```

##### TeFak

```{r TeFak_vis}
TeFak_1 <- ggplot(as.data.frame(TeFak$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl1)) + # min
  geom_line(aes(y = max_vec_cl1)) + # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl1,
    ymax = max_vec_cl1),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl2), col = "#b58900", size = 0.5) +
  # density
  geom_point(data = density_cl1_TeFak,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("First Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 250000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
TeFak_1 <- ggMarginal(TeFak_1, type = "density", margins = "y")

TeFak_2 <- ggplot(as.data.frame(TeFak$main_graph), aes(x = time)) +
  # filled area
  geom_line(aes(y = min_vec_cl2)) + # min
  geom_line(aes(y = max_vec_cl2))+ # max
  geom_ribbon(aes(
    x = time,
    ymin = min_vec_cl2,
    ymax = max_vec_cl2),
  fill = "gray",
  alpha = 0.4) +
  # centre
  geom_line(aes(y = cl1), col = "#b58900", size = 0.5) +
  # marginal density
  geom_point(data = density_cl2_TeFak,
             aes(x = as.POSIXct("2019-01-01 01:00:00"), y = avg), col = NA) +
  # effects
  ggtitle("Second Cluster") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0, 250000)) +
  scale_x_datetime(labels = date_format("%H:%M")) +
  labs(x = "Time of day",
       y = "Consumption in kWh")
TeFak_2 <- ggMarginal(TeFak_2, type = "density", margins = "y")

ggarrange(
  TeFak_1, TeFak_2,
  ncol = 2, nrow = 1,
  widths = c(1.3, 1.1)
)

ggsave("./graphs/TeFak_cluster_profiles.png",
       dpi = 320,
       width = 16,
       height = 5,
       units = "cm")
```

# test

```{r testield}
test_3 <- cluster_df(data_wide[data_wide$location == "TechnologieFabrik",2:97], TeFak_cluster$`k-means`)

test <- data_long[1:96, "time"]
class(test$time)
test_time <- hm(test$time)
class(test_time)


seq.POSIXt(as.POSIXct(Sys.Date()-(1/12)), as.POSIXct(Sys.Date()+(11/12)), by = "15 min")[1:96]
datetime <- seq(from = as.POSIXct("2019-01-01", tz = "GMT"), length.out = 96, by = "15 min")

class(rownames(test_3$main_graph))

test_3$main_graph
rownames(test_3$main_graph)
```

# debug

```{r debug}
data <- data_wide[data_wide$location == "TechnologieFabrik",]
cluster_data <- cluster_df$TeFak

data <- data %>%
    mutate(cluster = cluster_data)
  
  # change back to long format
  data_long <- data %>%
    pivot_longer(
      cols = c(-date,-cluster,-location),
      names_to = "time",
      values_to = "Verbrauch"
    )

  # add meta information
  setDT(data_long)
  # weekdays
  data_long <- data_long[, dayOfWeek := weekdays(date, abbreviate = TRUE)]
  # calendar week
  data_long <- data_long[, calendarWeek := isoweek(date)]
  # month
  data_long <- data_long[, month := month(date)]
  # BDEW weekend
  data_long <- data_long[, weekend :=
                          ifelse(dayOfWeek == "Sun",
                                  "Sunday",
                                  ifelse(dayOfWeek == "Sat", "Saturday", "working day"))]
  # variable for BDEW-season
  data_long <- data_long[, BDEWSeason :=
                          ifelse(month >= 12 | month <= 2,
                                  "Winter",
                                  ifelse(month >= 6 & month <= 9, "Summer", "Transition"))]
  # hour variable
  data_long <- data_long[, hour := as.numeric(substr(time, 1, 2))]
  
  # reorder column for better looking data frame
  setcolorder(
    data_long,
    c(
      "date",
      "location",
      "cluster",
      "Verbrauch",
      "BDEWSeason",
      "month",
      "calendarWeek",
      "dayOfWeek",
      "weekend",
      "hour",
      "time"
    )
  )
  
  # evaluation
  # location <- matrix(data = NA,
  #                    ncol = length(unique(data_long$cluster)),
  #                    nrow = length(unique(data_long$location)))
  # month <- matrix(data = NA,
  #                 ncol = length(unique(data_long$cluster)),
  #                 nrow = length(unique(data_long$month)))
  # calendarweek <- matrix(data = NA,
  #                        ncol = length(unique(data_long$cluster)),
  #                        nrow = length(unique(data_long$calendarWeek)))
  # weekday <- matrix(data = NA,
  #                   ncol = length(unique(data_long$cluster)),
  #                   nrow = length(unique(data_long$dayOfWeek)))
  weekend <- matrix(data = NA,
                    ncol = length(unique(data_long$cluster)),
                    nrow = length(unique(data_long$weekend)))
  BDEWSeason <- matrix(data = NA,
                       ncol = length(unique(data_long$cluster)),
                       nrow = length(unique(data_long$BDEWSeason)))
  
  # fill tables
  for (i in 1:length(unique(data_long$cluster))) {
    df <- data_long[data_long[, cluster == i]]
    # month
    # month[, i] <-
    #   table(factor(df$month, levels = 1:12)) /
    #   table(factor(data_long$month, levels = 1:12))
    # rownames(month) <- names(table(factor(df$month, levels = 1:12)))
    # # calenderweek
    # calendarweek[, i] <-
    #   table(factor(df$calendarWeek, levels = 1:53)) /
    #   table(data_long$calendarWeek)
    # rownames(calendarweek) <- names(table(factor(df$calendarWeek, levels = 1:53)))
    # # day of the week
    # weekday[, i] <-
    #   table(factor(df$dayOfWeek, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) /
    #   table(data_long$dayOfWeek)
    # rownames(weekday) <-
    #   names(table(factor(df$dayOfWeek, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))))
    # weekend
    weekend[, i] <-
      table(factor(df$weekend, levels = c("Saturday", "Sunday", "working day"))) /
      table(data_long$weekend)
    rownames(weekend) <- names(table(factor(df$weekend, levels = c("Saturday", "Sunday", "working day"))))
    # BDEW-Season1
    BDEWSeason[, i] <-
      table(factor(df$BDEWSeason, levels = c("Summer", "Transition", "Winter"))) /
      table(data_long$BDEWSeason)
    rownames(BDEWSeason) <- names(table(factor(df$BDEWSeason, levels = c("Summer", "Transition", "Winter"))))
  }
```